\section{Experiments}

\subsection{Dataset}


\textbf{Publications dataset:} The \textit{aminer} citation dataset\footnote{\url{https://aminer.org/citation}} V8 (2016-07-14) is extracted from DBLP, ACM, and other sources. It contains 3,272,991 papers and 8,466,859 citation relationships for 1,752,443 authors, who published in 10,436 venues, from 1930 to 2016. Each paper is associated with abstract, authors, year, venue, and title. \amin{We consider only those papers published since 1996, which includes X papers and Y authors.} Authors in \cite{sun2011ASONAM} used a similar dataset but considered only authors with more than 5 publications. We generate two datasets: one that contains all publications, and one that considers authors with at least 5 papers. We consider $k=3, 5, and 10$ different time intervals for the dynamic analysis. In our evaluation, we execute the learned model on the last interval to measure the prediction accuracy.

%The ml-latest-small\footnote{\url{http://files.grouplens.org/datasets/movielens/ml-latest-small-README.html}} dataset describes 5-star rating and free-text tagging activity from MovieLens\footnote{\url{https://movielens.org/}}, a movie recommendation service. It contains 100004 ratings and 1296 tag applications across 9125 movies. These data were created by 671 users between January 09, 1995 and October 16, 2016. This dataset was generated on October 17, 2016.

\textbf{Movies dataset:} The RecSys HetRec 2011 movie data set \cite{Cantador:RecSys2011} is an extension of MovieLens10M dataset, published by GroupLeans research group \footnote{\url{http://www.grouplens.org}} that links the movies of MovieLens dataset with their corresponding web pages at Internet Movie Database (IMDb\footnote{\url{http://www.imdb.com}}) and Rotten Tomatoes\footnote{\url{http://www.rottentomatoes.com}} movie review systems. It contains information of 2,113 users, 10,197 movies, 20 movie genres (avg. 2.04 genres per movie), 4,060 directors, 95,321 actors (avg. 22.78 actors per movie), 72 countries, 855,598 ratings (avg. 404.92 ratings per user, and avg. 84.64 ratings per movie), and 13,222 tags (avg. 22.69 tas per user, avg. 8.12 tas per movie).




\subsection{Baseline methods}

Considering the effect of time-wise data decomposition. What if we shorten timespans of each $G_t$? The extreme is having only one graph or having it for each year. Can we find a trade-off?

Heterogeneous non-temporal - Collection of PathSim (PathCount, NormalPCount, RandomWalk, Symmetric random walk)
Homogeneous non-temporal (Katz, Jaccard)
Homogeneous temporal (Katz, Jaccard)

\begin{enumerate}
    \item We use prediction error to evaluate the inference accuracy. Given the training graph G1, . . . , Gt, prediction error is defined as... Therefore, a smaller prediction error indicates better inference accuracy.
    
    \item For link prediction accuracy, we use Area Under Curves
(both Receiver Operating Characteristic (ROC) and Precision-
Recall (PR) curves), termed as AUCROC and AUCPR.

    \item NDCG
    
    \item Trade-off analysis (time overhead)
    
\end{enumerate}


\subsection{Comparing Classifiers}


\textbf{Statistical Comparison} In order to decide which of classifiers has a lower error rate, we perform McNemar's test, which assess the significance of the difference between two correlated proportions, such as might be found in the case where the two proportions are based on the same sample of subjects or on matched-pair samples.


\subsection{Discussion}

Our proposed technique can also be used in other applications. For example link recommendation 


predicting missing edges in graphs.

Vertex Recommendation similar to \cite{ou2016asymmetric} 

% visualize the network embeddings and features with t-SNE and use KL divergence to measure the performance

