\section{Introduction}
\label{Sec:Introduction}

% what is link prediction problem? what is the usages of link prediction?

The goal of link prediction in a social network graph \cite{liben2007link} is to estimate the likelihood of the relationship between two nodes in future, based on the observed network. Recommending such future connections have multiple applications such as friendship, item, or ad suggestions, network completion, or biological applications such as predicting protein-protein interactions.

% challenges in heterogeneous link prediction, what is not covered? temporal and hero?

Traditional link prediction techniques \cite{liben2007link}\amin{more citations} consider social networks to be homogeneous, i.e., graphs with only one type of edges and nodes. However, most real-world social networks, such as Twitter, Facebook, and DBLP, are heterogeneous, i.e., they have multiple relation and node types. For example, in a bibliographic network there are different types of nodes such as authors, papers, and venues, and different types of edges such as write, cite and publish. There are limited number of works that focused on this problem. For example, the probabilistic latent tensor factorization model... Recent works, such as \cite{sun2011pathsim}, investigated this problem. However, such techniques do not consider the dynamics of social networks and ignore sequence of network snapshots. 
\amin{make sure about these citations}
\cite{Zhu2016} \cite{sun2011pathsim} \cite{Sun:2012:HRP:2124295.2124373}  \cite{huang2016meta} \cite{wang2016relsim} \cite{sun2013pathselclus} \cite{sun2011ASONAM} \cite{Yang2012} \cite{liben2007link}


In this work we study the problem of temporal and heterogeneous link prediction, that can be stated as follows: \textit{Given a dynamic heterogeneous information network graph G (i.e., network with different types of nodes and links, attached with timestamps), how can we predict the future graph structure?}



\subsection{Motivation}

\amin{Motivate the problem by a real example and show the points made in this para.}

The link prediction problem for homogeneous networks has been studied in the past \cite{liben2007link}\amin{more citations}. However most real social networks are heterogeneous and relations between different entities have different semantic meanings. Thus techniques for homogeneous networks can not be directly applied on heterogeneous ones. A few works, such as \cite{sun2011pathsim,sun2011ASONAM}, investigated this problem, however, they do not consider the dynamics of social networks and ignore ignore sequence of network snapshots. On the other hand, it has ben shown that for homogenous network link prediction, incorporating temporal changes helps in a more accurate prediction \cite{Zhu2016}. Previous work on temporal link prediction scarcely studied heterogeneousness of social networks and to the best of our knowledge, the problem of relationship prediction for dynamic heterogeneous networks was not studied before.


\subsection{Contributions}

The main contributions of our work include:

\begin{itemize}

\item We present a technique, called \texttt{RelationPredict}, that predicts a target relationships between two nodes of given types;

\item An evaluation of the accuracy and performance of the proposed algorithm on real social network data.

\end{itemize}


